---
title: "Name of Experiment"
authors:
- name: Johannes Schantl
- name: David Blanchard
- name: Lisa Deckert
- name: Christof Stocker
authorshort: Feature Selection Comparision
output:
  pdf_document:
    highlight: tango
    keep_tex: yes
    number_sections: yes
    pandoc_args: --listings
    template: config/custom.latex
    toc: no
    toc_depth: 2
  html_document:
    fig_caption: yes
    highlight: tango
    number_sections: yes
    toc: no
  word_document: default
csl: config/elsevier-harvard.csl
bibliography: references.bib
sub_title: Experiment Documentation
---
```{r, include=FALSE}
rm(list = ls())
wdList <- strsplit(getwd(),"/")[[1]]
lastDir <- wdList[length(wdList) - 1]
if(lastDir == "experiments") {
  isMarkdown <- TRUE
  source('config/knitr-settings.R')
} else {
  isMarkdown <- FALSE
}
```

# Executive Summary

Short summary about the intention and the main results of this experiment

# Background

Short description where the experiment fits taxonomy wise (big picture background)

## Method(s)

Theoretical background to the method under test

## Dataset(s)

Information about the dataset. What makes it hard or easy to deal with, etc

## Related Work

Point to related work that deals with the same method and/or did a similar analysis
Point to applications of the method.

# Installation

Everything one needs to know to run the experiment

## Dependencies

The following R libraries have been used throughout the
analysis process and are required in order to reproduce the results.

You can import them using the ``library`` function.

```{r, echo=FALSE, message=FALSE, results='hide'}
# If a package is not yet installed, it will be installed automatically
options(repos = c(CRAN = "http://cran.rstudio.com/"))
libraryAutoInst <- function(package, ...) {
  if(!require(package, character.only = T)) 
    install.packages(package)
  library(package, character.only = T, ...)
}

# First import all the required libraries.
# I do that in this untypical way to support automatic creation of the dpendencie list
requiredLibraries <- c("ggplot2", "ggthemes", "dplyr", "data.table", "pander", "knitr")
invisible(lapply(requiredLibraries, libraryAutoInst))

## Set global settings for theme and color
theme_set(theme_bw())
```

```{r, echo=FALSE, message=FALSE, results='asis'}
# Print a markdown list of all the required libraries with some metadata
PrintLibrary <- function(x) {
  desc <- packageDescription(x)
  if(is.null(desc$URL)) desc$URL <- paste("https://www.google.at/search?q=R package", x)
  pUrl <- first(first(strsplit(desc$URL, ";|,"))) # avoid problems if multiple URLs are listed
  paste("* [", x, "](", pUrl,") (v", desc$Version,"): ", desc$Title,"\n", sep="")
}
cat(paste(sapply(requiredLibraries, PrintLibrary), collapse = ""))
```

Concerning R itself, we used **`r version$version.string`**.


# Experiment Design

How the experiment is set up as well as why it is set up this way.
Point out weak points

# Results

Show the numerical results and plots. Describe everything you see as you see it (no judging at this point)

# Discussion

Interpret the results using your background knowledge. Make it clear if you speculate; there is no shame in it as long as you are honoest about it.

\newpage

# References
